%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.


\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Almaas Shaikh}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:almaas0123@gmail.com}{almaas0123@gmail.com} | \href{tel:9408145797}{94081 45797}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Perfect Associates (via ST)}
\descript{| Product Owner}
\location{Oct 2022 – Present | Ahmedabad}
\vspace{\topsep}
\begin{tightemize}
\item Product Owner for a B2B e-commerce platform and ERP in the mobile parts industry.
\item Led requirements gathering and solution discovery, aligning with MACH principles and business goals.
\item Developed prioritised roadmaps with cross-functional teams and stakeholders.
\item Managed API integrations with insurance, logistics, and payment providers, improving transaction processing by 20\%.
\item Implemented a 3P RPA system in the warehouse, reducing handling costs by 20\% and enabling 5K+ daily order picking.
\item Led migration from monolith to microservices, improving feature delivery and uptime.
\item Created requirement documents, user stories, UML-BPMN diagrams, and managed UAT with stakeholder showcases.
\item Directed systems integration testing for seamless releases.
\item Facilitated backlog grooming with dev and QA teams, ensuring timely delivery.
\item Implemented continuous feedback loops for process improvement.
\end{tightemize}
\sectionsep

\runsubsection{Steamroll Technologies}
\descript{| Product Owner / Business Analyst}
\location{Jul 2018 – Oct 2022 | Ahmedabad}
\begin{tightemize}
\item Delivered 10+ enterprise IT projects, overseeing requirements, roadmaps, and cross-functional coordination.
\item Presented scope and deliverables to senior bureaucrats for G2G and G2B projects.
\item Drafted RFPs and evaluated vendor proposals for strategic selection.
\item Led client engagement across pre- and post-sales, increasing satisfaction by 30\%.
\item Facilitated Agile ceremonies: sprint planning, reviews, stand-ups, and backlog refinement.
\item Recommended process optimizations using BPMN/UML diagrams, boosting enterprise efficiency.
\item Transitioned teams to Agile tools (Jira, Confluence) for better project tracking and communication.
\end{tightemize}
\sectionsep

\runsubsection{Empowering CPO}
\descript{| Business Analyst}
\location{Jan 2018 – Jun 2018 | Ahmedabad}
\begin{tightemize}
\item Conducted spend analysis, achieving a 12\% cost reduction on a \$150K budget.
\item Performed competitive research for GTM positioning and pricing.
\item Advised global CPG and Aviation clients on procurement strategies.
\item Developed category-specific strategies through data and market research, enhancing partner selection.
\end{tightemize}
\sectionsep

\runsubsection{Gujarat Agro Industries Corporation Ltd.}
\descript{| Management Trainee}
\location{Jul 2017 – Sep 2017 | Gandhinagar}
\begin{tightemize}
\item Reviewed ERP and mobile app implementation, improving usability.
\item Assisted in financial data analysis for insurance products and pricing forecasts.
\item Developed credit policy that reduced late payments by 20\%.
\end{tightemize}
\sectionsep

\runsubsection{Peerbits Solutions}
\descript{| Content Writer}
\location{May 2016 – Aug 2016 | Ahmedabad}
\begin{tightemize}
\item Improved web traffic by 25\% and CTR by 30\% via 20+ blog posts.
\item Conducted keyword research to enhance SEO.
\item Created persuasive content, increasing average page visit durations.
\end{tightemize}
\sectionsep

\runsubsection{RapidOps Inc.}
\descript{| Software Engineer Intern}
\location{Jan 2016 – Apr 2016 | Ahmedabad}
\begin{tightemize}
\item Developed custom BigCommerce APIs using MEAN stack and Apache Solr.
\item Optimized website performance, cutting load times by 40\%.
\item Participated in code reviews and created technical documentation.
\end{tightemize}
\sectionsep


\section{Experience}
\runsubsection{TecStub India LLP}
\descript{| Business Analyst}
\location{Nov 2023 – Oct 2024 | Ahmedabad}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed a cloud-based solution to automate and enhance the engineering process for network installation using AWS and Python.
\item Worked with other teams to create a system to collect and visualize telemetry data of network elements in real time using AWS, Python, and DOMO.
\item Consulted with other teams to jump start cloud-technology adoption and solutions throughout the company.
\item Contributed to initial planning for optics-alignment system utilizing AWS, reinforcement learning, and an IoT architecture.
\end{tightemize}
\sectionsep

\runsubsection{Company B}
\descript{| Intern }
\location{Feb 2017 – Nov 2017 | Somewhere, XX}
\begin{tightemize}
\item Coordinated with multiple departments to lead a software product evaluation resulting in a fit-for-purpose verdict and provided a recommendation on moving forward.
\item Organized meetings with the vendor to receive in-depth product information and answers to cross-departmental questions.
\item Participated on the Web Development Taskforce to provide AngularJS sites to internal customers.
\item Participated in an internal CodeJam to prototype a blockchain application for managing a model supply-chain.
\item Worked with a team to plan executive visit and team-building exercise for 200 employees.
\end{tightemize}
\sectionsep

\runsubsection{My University ITS}
\descript{| Assistant Support Specialist }
\location{Aug 2015 – Oct 2016 | Somewhere, XX}
\begin{tightemize}
\item Interacted with clients to assess their problems and implement a solution in an efficient, friendly manner.
\item Prepared workstations and laptops for future use by company employees.
\item Created scripts to automate common tasks and increase productivity.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Space Robotics Team}
\descript{| Path-Planning Lead}
\location{Jan 2018 – Present | Somewhere, XX}
\begin{tightemize}
\item Spearhead the development effort for the path-planning functionality of a team of three robots.
\item ROS provides movement servers and the planning is being implemented in Python to allow for fully-autonomous operation.
\end{tightemize}
\sectionsep

\runsubsection{Chit Chat}
\descript{| Class Project for Distributed Client-Server Programming}
\location{Jan 2018 – May 2018 | Somewhere, XX}
\begin{tightemize}
\item Lead the development of \textbf{\href{https://github.com/user/repo}{Chit Chat}}, an anonymous chat application created as a class project.
\item Chit Chat provides real-time communication while utilizing a PHP backend and AngularJS frontend.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
% \location{Jan 2014 – Jan 2015 | Ithaca, NY}
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.
% \sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COMMUNITY SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Community Service}

% \begin{tabular}{rll}
% 2013 -- 2018    & Tennessee     & St. Baldrick's Foundation\\
% 2014 -- 2017	& Tennessee     & American Cancer Society's Hope Lodge\\
% 2013 -- 2015    & Tennessee     & Habitat for Humanity\\
% 2011 -- 2015    & Tennessee     & Special Olympics\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies}

% \begin{tabular}{rll}
% 2018 -- 2018    & National      & Association of Computing Machinery (ACM)\\
% 2017 -- 2019	& National      & Scrum Alliance Certified ScrumMaster\\
% 2015 -- 2019    & University    & Shackouls Honors College\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards}
% \begin{tabular}{rll}
% 2015        & 99\textsuperscript{th} percentile & National Merit Scholarship Finalist\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications}
% \renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}

A strategic PO \& BA with a passion for leading digital transformation in complex environments like E-commerce, ERP, \& the Public Sector. Thrives on bridging the gap between business goals and technical execution, fostering collaboration to optimize workflows and deliver user-centric products. A quick learner dedicated to creating tangible business value.
\sectionsep

\section{Education}

\subsection{Post Graduation}
\descript{MBA - dual specialisation Finance \& Marketing}
\location{2018 | BKSBM, GU}
\descript{MA - Sociology}
\location{expected 2026 | MSO, IGNOU}
\sectionsep

%\subsection{Master of Business Administration}
%\descript{MBA - dual specialisation Finance \& Marketing}
%\location{2018 | BKSBM, GU}
%\sectionsep

\subsection{Graduation}
\descript{BE in Computer Science}
\location{2016 | AIT, GTU}
Dean's List (All Semesters) \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Key Skills}

\subsection{Product \& Agile}
Product Roadmapping\\
Stakeholder Management \& Alignment\\
User Persona \& Journey Mapping\\
Market Research \& Competitive Analysis\\
Agile \& Scrum Methodologies\\
User Story \& Epic Creation\\
Backlog Grooming \& Prioritisation\\
% API Product Management\\

\sectionsep

\subsection{Business Analysis}
Requirements Elicitation \& Management\\
Process Modelling\\
Gap Analysis \& Solution Design\\
Documentation\\
User Acceptance Testing (UAT)\\ABC 
Cross-Functional Team Leadership\\
\sectionsep

\subsection{Tools \& Tech}

Jira - Confluence \textbullet{} Trello \textbullet{} Lucidchart\\
Figma \textbullet{} GitHub \textbullet{} Productboard Aha\\
SQL \textbullet{} Power BI \textbullet{} GA \textbullet{} Mixpanel\\
\sectionsep

%\subsection{Tools \& Tech}
%\textbf{Agile \& PM:} Jira \textbullet{} Confluence \textbullet{} Trello \\
%\textbf{Analysis \& Design:} Miro \textbullet{} Lucidchart \textbullet{} MS Visio \textbullet{} Figma \\
%\textbf{Data \& Analytics:} SQL \textbullet{} Tableau \textbullet{} Power BI \textbullet{} Google Analytics \\
%\textbf{Technical Concepts:} API Integration \textbullet{} Microservices Architecture \textbullet{} RPA \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Competitive Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Competitive Awards}
Open Gov Data Hackathon\\
Smart India Hackathon\\
National Case Studies (under publication)\\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links}
%LinkedIn://  \href{https://www.linkedin.com/}{\bf johndoe}
%\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}