% Almaas Shaikh - Strategic Business Analyst Resume (XeLaTeX)
% Paste into Overleaf or local editor and compile with XeLaTeX

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{multicol}

% Fonts
\setmainfont{TeX Gyre Heros} % or another modern sans font

% Colors
\definecolor{primary}{HTML}{2E86C1} % Navy blue
\definecolor{graytext}{gray}{0.4}

% Section formatting
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}
\titlespacing{\section}{0pt}{10pt}{4pt}

% Resume bullets
\newcommand{\resumeItem}[1]{\item \textbullet\ #1}
\newcommand{\resumeSubItem}[1]{\item[--] #1}

\pagestyle{empty}

\begin{document}

% ==== Header ====
\noindent
{\LARGE \textbf{Almaas Shaikh}} \\[2pt]
\href{mailto:almaas0123@gmail.com}{almaas0123@gmail.com} $\vert$ +91-88491 40665 $\vert$ Ahmedabad $\vert$
\href{https://linkedin.com/in/almaasshaikh}{linkedin.com/in/almaasshaikh} \\[6pt]
\textcolor{graytext}{Strategic Business Analyst with 8+ years in civic tech, payments, logistics, and procurement. Expert in Agile delivery, partner API integrations, and public sector systems. Converts ambiguity into user-centric roadmaps and measurable results.}

% ==== Skills ====
\section*{Core Skills}
\begin{multicols}{2}
\textbf{Product \& Strategy}
\begin{itemize}[leftmargin=*,noitemsep]
  \item Product Roadmapping, Partner APIs
  \item Market \& Competitor Analysis
  \item User Journey Mapping
\end{itemize}

\textbf{Agile \& Execution}
\begin{itemize}[leftmargin=*,noitemsep]
  \item Epics, User Stories, Acceptance Criteria
  \item Backlog Grooming, UAT
  \item Process Modeling (BPMN, Gap Analysis)
\end{itemize}

\textbf{Tools}
\begin{itemize}[leftmargin=*,noitemsep]
  \item Jira, Confluence, Productboard
  \item Figma, Miro, Lucidchart, Notion
  \item SQL, Power BI, Looker Studio, Mixpanel
\end{itemize}
\end{multicols}

% ==== Experience ====
\section*{Professional Experience}

\textbf{CIVIC TECH (NDA)}\hfill \textit{Business Analyst Consultant}\\
\textit{Nov 2024 – Present | Ahmedabad}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Unified feedback \& backlog system across stakeholders increased roadmap confidence by 50\%.}
  \resumeItem{Improved underserved onboarding flows, reducing drop-offs by 33\%.}
  \resumeItem{Led kiosk/mobile UAT, resolving 10+ major usability blockers pre-launch.}
\end{itemize}

\textbf{TecStub} \hfill \textit{Business Analyst}\\
\textit{Nov 2023 – Oct 2024 | Ahmedabad}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Drove monolith-to-microservices shift, cutting incidents by 40\%, enabling weekly deployments.}
  \resumeItem{Automated warehouse ops via RPA, reducing handling costs by 20\%.}
  \resumeItem{Built backlog of 200+ stories with BPMN flows, reducing dev rework by 30\%.}
  \resumeItem{Integrated 10+ partner APIs, improving transaction throughput by 20\%.}
\end{itemize}

\textbf{Steamroll Technologies} \hfill \textit{Business Analyst}\\
\textit{Jul 2018 – Oct 2023 | Ahmedabad}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Launched G2C/G2B GRAS payment portal used by 3K+ users, cutting payment queries by 40\%.}
  \resumeItem{Drove Agile transition via Jira, Confluence, and team coaching, speeding delivery by 25\%.}
  \resumeItem{Managed RFP to vendor finalization, delivering project 15\% under budget.}
  \resumeItem{Increased client satisfaction by 30\% via executive reporting and support.}
\end{itemize}

\section*{Early Experience}
\textbf{Empowering CPO} \hfill \textit{Business Analyst}\\
\textit{Jan – Jun 2018}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Saved \$18K (12\%) on \$150K procurement via strategic cost modeling.}
\end{itemize}

\textbf{Gujarat Agro Industries Corp.} \hfill \textit{Mgmt Trainee}\\
\textit{Jul – Sep 2017}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Designed credit policy that reduced late payments by 20\%.}
\end{itemize}

\textbf{Peerbits Solutions} \hfill \textit{Content Writer}\\
\textit{May – Aug 2016}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Increased web traffic by 25\% with SEO-rich blog content.}
\end{itemize}

\textbf{RapidOps Inc.} \hfill \textit{Software Intern}\\
\textit{Jan – Apr 2016}
\begin{itemize}[leftmargin=*,noitemsep]
  \resumeItem{Built custom APIs in MEAN stack, improving site load time by 40\%.}
\end{itemize}

% ==== Education ====
\section*{Education}
\textbf{MBA – Finance \& Marketing} \hfill BKSBM, Gujarat University, 2018\\
\textbf{BE – Computer Science} \hfill AIT, GTU, 2016

% ==== Awards ====
\section*{Awards \& Recognition}
\begin{itemize}[leftmargin=*,noitemsep]
  \item Winner – OpenGovData Hackathon
  \item Finalist – Smart India Hackathon
  \item National Case Study Competitions (under publication)
\end{itemize}

\end{document}
